---
title: "Untitled"
output: html_document
date: "2025-12-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

## make predictions by demographic group and identify winner for Flourish map

library(here)
library(tidyverse)
install.packages("ggridges")
library(ggridges)

all_preds <- read_csv(here("overall", "dec2025_mrp_preds.csv"))
age_preds <- read_csv(here("age", "dec2025_mrp_preds.csv"))


all_preds %>%
  left_join(age_preds %>% select(const_name, age_level), 
            by = "const_name") %>%
  ggplot(aes(x = WNV, y = as.factor(age_level))) + 
  geom_density_ridges(scale = 0.9) +
  labs(y = "Age Level", x = "WNV Vote Share") +
  theme_minimal()


mrp_preds_edu <- read_csv("degree/dec2025_mrp_preds.csv") 


mrp_edu_pct <- mrp_preds_edu %>% 
#  select(-WNV) %>% 
  mutate(total = rowSums(pick(Conservative:`Scottish National Party (SNP)`), na.rm=TRUE), 
         across(Conservative:`Scottish National Party (SNP)`, ~ .x/total * 100))  %>% 
  pivot_longer(Conservative:`Scottish National Party (SNP)`, names_to="party", values_to = "pct") %>%
  group_by(const_name, edu_level) %>% 
  mutate(winner = party[which.max(pct)]) %>% 
  pivot_wider(names_from=party, values_from=pct) %>% 
  rename(Constituency = const_name) %>% 
  select(Constituency, Conservative:`Scottish National Party (SNP)`, winner, edu_level)



mrp_preds_as <- read_csv("age_sex/dec2025_mrp_preds.csv") 

mrp_preds_as <- mrp_preds_as %>% 
  filter(age_level %in% c("18-24")) %>% 
 # select(-age_level) %>%)
 ## select(-WNV, -age_level) %>% 
  group_by(const_name, sex_level) %>% 
  summarise(across(Conservative:`Scottish National Party (SNP)`, \(x)sum(x, na.rm=TRUE)), .groups="drop") %>% 
  pivot_longer(Conservative:`Scottish National Party (SNP)`, names_to="party", values_to = "pct") %>%
  group_by(const_name, sex_level) %>% 
  mutate(pct = pct/sum(pct) * 100) %>%
  mutate(Winner = party[which.max(pct)]) %>% 
  pivot_wider(names_from=party, values_from=pct) %>% 
  rename(Constituency = const_name) %>% 
  select(Constituency, Conservative:`Scottish National Party (SNP)`, Winner, sex_level)

mrp_preds_male <- mrp_preds_as %>% 
  filter(sex_level == "Male") %>% 
  ungroup %>% 
  select(-sex_level)

mrp_preds_female <- mrp_preds_as %>% 
  filter(sex_level == "Female") %>% 
  ungroup %>% 
  select(-sex_level)

### woould not  vote  for differnt age groups by gender 


## for 55-64 

mrp_preds_as <- mrp_preds_as %>% 
  filter(age_level %in% c("55-64")) %>% 
 # select(-age_level) %>%)
  select(-WNV, -age_level) %>% 
  group_by(const_name, sex_level) %>% 
  summarise(across(Conservative:`Scottish National Party (SNP)`, \(x)sum(x, na.rm=TRUE)), .groups="drop") %>% 
  pivot_longer(Conservative:`Scottish National Party (SNP)`, names_to="party", values_to = "pct") %>%
  group_by(const_name, sex_level) %>% 
  mutate(pct = pct/sum(pct) * 100) %>%
  mutate(Winner = party[which.max(pct)]) %>% 
  pivot_wider(names_from=party, values_from=pct) %>% 
  rename(Constituency = const_name) %>% 
  select(Constituency, Conservative:`Scottish National Party (SNP)`, Winner, sex_level)

mrp_preds_male_old <- mrp_preds_as %>% 
  filter(sex_level == "Male") %>% 
  ungroup %>% 
  select(-sex_level)

mrp_preds_female_old <- mrp_preds_as %>% 
  filter(sex_level == "Female") %>% 
  ungroup %>% 
  select(-sex_level)





##"25-34"

write.csv(mrp_preds_male, here("graph_data", "young_men_2.csv"), row.names = FALSE)


write.csv(mrp_preds_female, here("graph_data", "young_women_2.csv"), row.names = FALSE)



table(mrp_preds_male$Winner)


table(mrp_preds_female$Winner)


mrp_preds <- read_csv("overall/overlay_preds.csv") 

colnames(mrp_preds) <- gsub("\\.", " ", colnames(mrp_preds))

margin <- mrp_preds %>% 
 # select(-WNV) %>% 
  pivot_longer(Conservative:`Scottish National Party  SNP `, names_to="party", values_to = "vote") %>%
  group_by(Constituency) %>% 
  mutate(pct = vote/sum(vote, na.rm=TRUE) * 100) %>% 
  summarise(winner = party[which.max(pct)], 
         mov = rev(diff(sort(pct)))[1]) %>% 
  mutate(margin = case_when(
    mov < 5 ~ "Less than 5%",
    mov >=5 & mov < 10 ~ "5-10%",
    mov >=10 & mov < 15 ~ "10-15%",
    mov >=15 & mov < 20 ~ "15-20%", 
    mov >= 20 & mov <= 25 ~ "20-25%",
    mov > 25 ~ "More than 25%"
  ), 
  margin = factor(margin, levels = c("Less than 5%", "5-10%", "10-15%", "15-20%", "20-25%", "More than 25%"))) 




table(margin$margin)


